---
title: "week3assignment"
author: "uzma"
date: "3 December 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##NLP week3 assignment

load libraries and data

```{r library}
library(NLP)
library(tm)
library(stringi)
library(RWeka)
library(ggplot2)
library(wordcloud)
library(RColorBrewer)
library(stringr)
library(dplyr)
library(tm)
library(stylo)
options(mc.cores=1)
```

for loading data

```{r debug}
conectionTwiter <- file('en_US.twitter.txt')
TwiterData <- readLines(conectionTwiter,encoding = 'UTF-8',skipNul = TRUE)
close(conectionTwiter)
conectionNews <- file('en_US.news.txt', open = 'r')
newsData <- readLines(conectionNews)
close(conectionNews)
conectionBlog <- file('en_US.blogs.txt',open = 'r')
BlogData <- readLines(conectionBlog)
close(conectionBlog)

library(tm)
nLines <- 5000
traindata <- nLines*2
testdata <- nLines





twiterIndex <- sample(TwiterData,nLines,replace = FALSE)

newsIndex <- sample(newsData,nLines,replace = FALSE)

BlogIndex <- sample(BlogData,nLines,replace = FALSE)

#Removing source data from environment
rm(TwiterData)
rm(newsData)
rm(BlogData)

#Creating a courpus from the character vector. 
sData<- c(twiterIndex,newsIndex,BlogIndex)
train <- gsub("[^a-zA-Z0-9 ]","",sData)[1:traindata]
test <- gsub("[^a-zA-Z0-9 ]","",sData)[traindata+1:testdata]


corpus_maker <- function (x,y){
      
      temp <- Corpus(VectorSource((x)))
      temp <- tm_map(temp, stripWhitespace)
      temp <- tm_map(temp, content_transformer(tolower))
      temp <- tm_map(temp, removePunctuation)
      temp <- tm_map(temp, removeNumbers)
      
      temp <- tm_map(temp,removeWords, stopwords("english"))
      
     
      data.frame(table(NGramTokenizer(temp,Weka_control(min=y, max=y))))
}

ngramOne <- corpus_maker(train,1)
ngramOne$Var1 <- as.character(ngramOne$Var1)
ngramOne$pred <- "n/a"
ngramOne <- ngramOne[order(-ngramOne$Freq),]
rownames(ngramOne) <- c(1:nrow(ngramOne))

ngramtwo <- corpus_maker(train,2)
ngramtwo$Var1 <- as.character(ngramtwo$Var1)
ngramtwo <- ngramtwo[order(-ngramtwo$Freq),]
rownames(ngramtwo) <- c(1:nrow(ngramtwo))
ngramtwo$word1 <-word(ngramtwo$Var1,1)
ngramtwo$word2 <- word(ngramtwo$Var1,2)

ngramthree <- corpus_maker(train,3)
ngramthree$Var1 <- as.character(ngramthree$Var1)
ngramthree <- ngramthree[order(-ngramthree$Freq),]
rownames(ngramthree) <- c(1:nrow(ngramthree))
ngramthree$word1 <-word(ngramthree$Var1,1)
ngramthree$word2 <- word(ngramthree$Var1,2)
ngramthree$word3 <- word(ngramthree$Var1,3)

ngramfour <- corpus_maker(train,4)
ngramfour$Var1 <- as.character(ngramfour$Var1)
ngramfour <- ngramfour[order(-ngramfour$Freq),]
rownames(ngramfour) <- c(1:nrow(ngramfour))
ngramfour$word1 <-word(ngramfour$Var1,1)
ngramfour$word2 <- word(ngramfour$Var1,2)
ngramfour$word3 <- word(ngramfour$Var1,3)
ngramfour$word4 <- word(ngramfour$Var1,4)

testgram_3 <- corpus_maker(test,3)
testgram_3$Var1 <- as.character(testgram_3$Var1)
testgram_3 <- testgram_3[order(-testgram_3$Freq),]
rownames(testgram_3) <- c(1:nrow(testgram_3))
testgram_3$word1 <- word(testgram_3$Var1,1)
testgram_3$word2 <- word(testgram_3$Var1,2)
testgram_3$word3 <- word(testgram_3$Var1,3)

n<-1
while(n<=nrow(testgram_3)){
  testgram_3$pred1[n]<-ngramtwo$word2[ngramtwo$word1==testgram_3$word2[n]][1]
  testgram_3$pred2[n]<-ngramthree$word3[ngramthree$word1==testgram_3$word1[n] & ngramthree$word2==testgram_3$word2[n]][1]
  n<-n+1  
}

testgram_3$correct1 <- ifelse(testgram_3$word3==testgram_3$pred1,1,0)
testgram_3$correct2 <- ifelse(testgram_3$word3==testgram_3$pred2,1,0)
head(testgram_3)

sum(testgram_3$correct1,na.rm = TRUE)/nrow(testgram_3)
sum(testgram_3$correct2,na.rm = TRUE)/nrow(testgram_3)

quiz2trigram <- corpus_maker("The guy in front of me just bought a pound of bacon, a bouquet, and a case of",3)

quiz2trigram$Var1 <- as.character(quiz2trigram$Var1)quiz2trigram <- quiz2trigram[order(-quiz2trigram$Freq),]
rownames(quiz2trigram) <- c(1:nrow(quiz2trigram))
quiz2trigram$word1 <-word(quiz2trigram$Var1,1)
quiz2trigram$word2 <- word(quiz2trigram$Var1,2)
quiz2trigram$word3 <- word(quiz2trigram$Var1,3)

head(quiz2trigram)

n<-1
while(n<=nrow(quiz2trigram)){
  quiz2trigram$pred1[n]<-ngramtwo$word2[ngramtwo$word1==testgram_3$word2[n]][1]
  quiz2trigram$pred2[n]<-ngramthree$word3[ngramthree$word1==testgram_3$word1[n] & ngramthree$word2==testgram_3$word2[n]][1]
  n<-n+1  
}

quiz2trigram$correct1 <- ifelse(quiz2trigram$word3==quiz2trigram$pred1,1,0)
quiz2trigram$correct2 <- ifelse(quiz2trigram$word3==quiz2trigram$pred2,1,0)
head(quiz2trigram)